Re-fit

### 2022-07-14 scripts/r/03_analyses_coding.Rmd

```{r comps}
assigned <- coding %>%
  select(team, animal, assigned_to) %>%
  distinct()

@@

```{r forest-plot}
msa_models %>% 
  unnest(sum) %>%
  filter(mod_name != "polymetme_brevirostrum_1_dur_cat") %>%
  mutate(
    typicality_lab = if_else(
      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
    ), 
    mod_name = fct_reorder(mod_name, estimate)
  ) %>% 
  ggplot(aes(x = estimate, y = mod_name)) + 
  geom_vline(xintercept = 0) +
  geom_segment(aes(x = estimate - se * 1.96, xend = estimate + se * 1.96, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") +
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```

>>>>

```{r comps}
assigned <- coding %>%
  dplyr::select(team, animal, assigned_to) %>%
  distinct()

@@

```{r forest-plot}
msa_models %>% 
  unnest(sum) %>%
  filter(mod_name != "polymetme_brevirostrum_1_dur_cat") %>%
  mutate(
    typicality_lab = if_else(
      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
    ), 
    mod_name = fct_reorder(mod_name, estimate)
  ) %>% 
  ggplot(aes(x = estimate, y = mod_name)) + 
  geom_vline(xintercept = 0) +
  geom_segment(aes(x = estimate - se * 1.96, xend = estimate + se * 1.96, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
  facet_wrap(typicality_lab ~ ., ncol = 2, scales = "free") +
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```

### 2022-07-14 scripts/r/04_refit/refit_tr.Rmd

# libs
library("here")
library("fs")
library("dplyr")
library("tidyr")
library("readr")
library("forcats")
library("ggplot2")
library("stringr")
library("strex")
library("purrr")
library("lme4")
library("brms")
library("broom")
library("broom.mixed")
library("readxl")
library("optimx")
library("MuMIn")
library("fda")
library("abind")
library("data.table")
library("magrittr")
library("tidyverse")

@@

# psittacula_scabriculus

```{r authors setup}

```{r their_models}

```{r refitting}

# eosipterus_pytyopsittacus

```{r authors setup}

```{r their_models}

```{r refitting}

# pseudopleuronectes_assasi

```{r authors setup}

```{r their_models}

```{r refitting}

@@

```{r their_models}

```{r refitting}

# ceratophrys_elephantotus

```{r authors setup}

```{r their_models}

```{r refitting}

# clione_dorsalis

```{r authors setup}

```{r their_models}

```{r refitting}

# aracana_bitatawa

```{r authors setup}

```{r their_models}

```{r refitting}

@@

# nestor_idahoensis

```{r authors setup}

```{r their_models}

```{r refitting}

# sphyrna_ellioti

```{r authors setup}

```{r their_models}

```{r refitting}

@@

# aratinga_lugubris

```{r authors setup}

```{r their_models}

```{r refitting}

>>>>

# libs
library(tidyverse)
library(brms)
library(readxl)

@@

@@

@@

@@
